### 2022-11-10 dissertation/chapters/08-results-old.tex
🚧 (results): WIP - Re-plotting case study

The statements made above conclude the successful working of the \Acs{BHH}. Both the perturbative element (through proxied heuristic update steps) and the selection mechanism (through Bayesian analysis) is shown to work successfully. Figure \ref{fig:results:case_study:iris:p_HgEC} shows the resulting output of the predictive model for each of the five entities in the heuristic pool. This predicted heuristic selection probability is used to parameterise a new categorical distribution from which the heuristics are finally sampled and (re)selected.

>>>>

The statements made above conclude the successful working of the \Acs{BHH}. Both the perturbative element (through proxied heuristic update steps) and the selection mechanism (through Bayesian analysis) is shown to work successfully. Figure \ref{fig:results:case_study:iris:p_HgEC} shows the resulting output of the predictive model for each of the five entities in the heuristic pool. This predicted heuristic selection probability is used to parameterise a new Categorical distribution from which the heuristics are finally sampled and (re)selected.
